\documentclass[a4paper, 11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{listings}
\usepackage[none]{hyphenat}
\lstset{basicstyle=\ttfamily,breaklines=true}

\title{Proposal for adding debugger on the Aa model}

\author{Titto Thomas}

\date{\today}

\begin{document}
\maketitle

\section*{Current implementation}
\label{sec:current}

\subsection*{In ccu.Aa}
\begin{itemize}
\item A \texttt{debug\_daemon} module that currently supports only reading register contents and memory. It also supports writing to the registers and memory as well.

\item In \texttt{ccu\_daemon} checks for the processor mode for \texttt{PROCESSOR\_DEBUG\_RESET}.
\end{itemize}

\section*{Proposed additions}
\label{sec:proposal}

\subsection*{In ccu}
\begin{itemize}
\item Pass the processor mode information ( \texttt{PROCESSOR\_DEBUG\_RESET} ) to the \texttt{teu} blocks for enabling breakpoint and watchpoint checks.

	\begin{itemize}
	\item replace the current single bit \texttt{single\_step\_mode\_selected} with a 2bit \texttt{processor\_mode\_selected}
	\end{itemize}

\item When there is a breakpoint / watchpoint hit informed by the \texttt{teu}, change the processor mode to single step mode ( \texttt{PROCESSOR\_SINGLE\_STEP\_RESET} ) and let the \texttt{teu} finish executing the current instruction.

\item Abort further instruction fetch and then transfer the control over to the \texttt{ccu\_daemon} and wait for a continue signal. If the gdb has detached then let the \texttt{teu} continue in normal mode, otherwise continue in debug mode.
\end{itemize}

\subsection*{In teu}
\begin{itemize}
\item Store 4 breakpoint and 4 watchpoint registers in the register file.

\item If debug mode is enabled then perform a check of calculated memory address with the currently active watchpoints in the \texttt{load\_store} and pass on the information to \texttt{iretire}.

\item \texttt{iretire} should stop execution and hand over the control to \texttt{teu} in case of any watchpoint hit ( informed by the \texttt{load\_store} ) or breakpoint hit ( by comparing breakpoint registers and current PC ) if debug mode is enabled.
\end{itemize}

\subsection*{In debug\_daemon}
\begin{itemize}
\item Wait for the control transfer from the \texttt{ccu} and then communicate with \textit{GDB software server} over pipes. Execute their commands like reading / writing to registers / memory and setting / clearing of watchpoints / breakpoints.

\item If the \textit{GDB software server} send a continue message, then inform the \texttt{ccu} to continue in debug mode.

\item If the \textit{GDB software server} send a detach / kill message, then inform the \texttt{ccu} to continue in normal mode.
\end{itemize}

\end{document}