%\documentclass{article}
\documentclass{book}

\usepackage{epsf}
\usepackage{pstricks}
\usepackage{enumitem}
% \usepackage[cm]{fullpage}
\usepackage{fullpage}
% \usepackage{hyperref}
% \usepackage[colorlinks=true,citecolor=brown,pagebackref=true,backref=true,hyperfigures=true,hyperfootnotes=true,hyperindex=true]{hyperref}

\usepackage{hyperref}
% \usepackage{minitoc}
% \usepackage{float}
% \usepackage[algo2e,boxruled,vlined]{algorithm2e}
%\usepackage[algo2e,boxruled,vlined,linesnumbered]{algorithm2e}
%\usepackage[algo2e,algoruled,linesnumbered]{algorithm2e}
%\usepackage[algo2e,tworuled,linesnumbered]{algorithm2e}

\hypersetup{colorlinks=true}
\hypersetup{citecolor=red}
\hypersetup{urlcolor=blue}
\hypersetup{pagebackref=true}
\hypersetup{backref=true}
\hypersetup{hyperfigures=true}
\hypersetup{hyperfootnotes=true}
\hypersetup{hyperindex=true}
% \hypersetup{pdfauthor=Abhijat Vichare}

\newrgbcolor  {darkgreen}    {.533     .8     .533}

%% Define a new floating environment for algorithms. See the LaTeX
%% wikibook.
%% March, 2020.
% \floatstyle{ruled}
% \restylefloat{table}
% \restylefloat{figure}
% \newfloat{algo}{tbph}{alg}
% \floatname{algo}{Algorithm}

\parindent 0in
\parskip 0.1in

% \def\codetoadd#1{%
% \framebox{%
%   \parbox{\textwidth}{%
%     #1%
%   }
% }
% \def\codetoadd#1{%
% \framebox{%
%   \begin{minipage}[h]{1.0\linewidth}
%     #1%    
%   \end{minipage}
% }

\def\note#1{%
  \framebox[\linewidth]{%
    \begin{minipage}[h]{0.95\linewidth}
      {\red \textbf{Note:}}\\%
      {\blue {#1}}
    \end{minipage}
  }
}
\def\attention#1#2{%
  \framebox[\linewidth]{%
    \begin{minipage}[h]{0.95\linewidth}
      {\red \textbf{#1}}\ %\\%
      {\blue {#2}}
    \end{minipage}
  }
}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\begin{document}
\title{64-bit ISA extensions to the AJIT processor}
\author{Madhav Desai}
\maketitle
\newpage
\parskip=0em
\tableofcontents
\newpage
\listoftables
\newpage
\parskip 0.1in

\chapter{The ISA Specification from IITB}
\label{chap:from:mpd:at:iitb}

\begin{center}
  \begin{tabular}[h]{|l|l|}
    \hline
    {\blue \textbf{ISA Version}}&{\red 2}\\
    %{\blue \textbf{Section below}}&{\red \ref{sec:isa:v2}}\\
    {\blue \textbf{Section below}}&{\red \ref{sec:isa:extns}}\\
    {\blue \textbf{ISA Version Date}}&{\red September 2020.}\\
    {\blue \textbf{Updated on}}&{\red December 17, 2020.}\\
    \hline
  \end{tabular}
\end{center}

\section{Overview}
\label{sec:Overview}

The AJIT processor implements the  Sparc-V8 ISA.  We propose to extend
this ISA to provide support for a native 64-bit integer datatype.  The
proposed  extensions use  the  existing instruction  encodings to  the
maximum extent possible.

All  proposed  extensions  are:   {\blue  Register  $\times$  Register
  $\rightarrow$  Register,Condition-codes}   type  instructions.   The
load/store instructions are not modified.

% All proposed extensions are:

% \centerline{Register $\times$ Register $\rightarrow$ Register,Condition-codes}

% type instructions.  The load/store instructions are not modified.

We list  the additional instructions  in the subsequent  sections.  In
each  case,  only the  differences  in  the  encoding relative  to  an
existing Sparc-V8 instruction are provided.

\attention{Note}{This  section records  the ISA  version 2  updates as
  received on September 2020.}

\subsection{Changes relative to Version 1}
\label{sec:changes:wrt:v1}

There has been some rationalization  of the instructions.  Further the
ASR register mappings have been updated.

Notes on instruction naming: V*  means a vector SIMD instruction

\subsubsection{Instruction Modifications}
\label{sec:insn:modified}

\begin{itemize}
\item Some instructions have been removed.

  \texttt{VFDIV VFSQRT}

\item Some instructions have been renamed.

  \begin{itemize}
  \item   \texttt{ADDDBYTER}    replaced   with   \texttt{ADDDREDUCE8}
    instruction encoding modified as shown later.

    Given [a1 a2 a3 ... a8] calculate (a1+a2+...+a8)
  \item    \texttt{ORDBYTER}    replaced   with    \texttt{ORDREDUCE8}
    instruction encoding modified as shown later.
  \item   \texttt{ANDDBYTER}    replaced   with   \texttt{ANDDREDUCE8}
    instruction encoding modified as shown later.
  \item   \texttt{XORDBYTER}    replaced   with   \texttt{XORDREDUCE8}
    instruction encoding modified as shown later.
  \item \texttt{VFADD} replaced with \texttt{VFADD32} opcode modified.

    Given  [x1  x2], [y1  y2]  of  single-precision numbers  calculate
    [(x1+y1) (x2+y2)] this becomes \texttt{VFADD32}

    Added  half-precision [x1  x2  x3  x4], [y1  y2  y3 y4]  calculate
    [(x1+y1) (x2+y2) ... (x4 + y4)] this becomes \texttt{VFADD16}
   \item \texttt{VFSUB} replaced with \texttt{VFSUB32} opcode modified.
   \item \texttt{VFMUL} replaced with \texttt{VFMUL32} opcode modified.
  \end{itemize}

\item Some instructions have been added.  Opcodes have been assigned (see
  below).

  \begin{tabular}[h]{p{.25\linewidth}p{.25\linewidth}p{.25\linewidth}p{.25\linewidth}}
  \texttt{ADDDREDUCE16}&\texttt{ORDREDUCE16}&\texttt{ANDDREDUCE16}&
  \texttt{XORDREDUCE16}\\
  \texttt{VFADD16}&\texttt{VFSUB16}&\texttt{VFMUL16}&~\\
  \texttt{FADDREDUCE16}&~&~&~\\
  \texttt{FSTOH}&\texttt{FHTOS}&~&~\\
  \texttt{VFHTOI16}&\texttt{VFI16TOH}&~&~
  \end{tabular}
  Instruction behaviour is described below.
\end{itemize}

\subsubsection{ASR mappings}
\label{sec:asr:mappings}


\texttt{ASR[31]} and \texttt{ASR[30]}  provide a free-running 64-bit counter
running on the processor clock (same as in AJIT32).

\texttt{ASR[29]} is intialized to processor ID field (writes to this
register are ignored).

The ancillary  state register \texttt{ASR[28]}  is interpreted
as a floating point configuration  register.  The bits of this
register are interpreted as follows:
\begin{tabbing}
  ~~~~~~~~\=~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \kill
  31:8 \> unused \\
  7:0  \>  half-precision exponent width
\end{tabbing}
This register is intialized to a value of 5 by default (as
per the IEEE half-precision format).  Valid values of the
exponent width are between 5 and 14.

IEEE half precision = 1 sign + 5 exp + 10 mantissa bits
would like\\ 		
\centerline{1 sign 08 exp 7 mantissa}
\centerline{1 sign 12 exp 3 mantissa}

\newpage
\section{ISA Extensions}
\label{sec:isa:extns}

The extensions to SPArc V8 for AJIT are described in this section.

% \input{../src/isa-v1-details}
This has been superseded by version 2 as below.

\section{ISA Version 2}
\label{sec:isa:v2}

\input{../src/isa-v2-details}

\newpage
\input{../src/binutils}
\input{../src/sisad}

\newpage
\input{../src/packaging}

\end{document}
