% Acknowledgement

\chapter*{Acknowledgement}

I would like to express my sincere gratitude toward my thesis advisor, Prof. Madhav P Desai for his guidance and encouragement throughout this work. His advice and suggestions were critical for the progress of the work and gave me an excellent opportunity to explore and push the boundaries. The methods and philosophies I learned from him will remain close to me throughout my professional life.


I would like to thank my colleagues Mr. Ashfaque Ahammed, Mr. Piyush Soni and Ms. Neha Karanjkar with whom I have collaborated during this project. The discussions we had was a great learning experience and provided me valuable inputs regarding the project.

I would also like to thank Ms. Krupa Bathia and all the students working with Prof. Madhav P Desai for their help during different stages of the project.


I would like thank the Electrical Engineering Department, IIT Bombay for providing me all the facilities and resources for research.

I would like to thank my friends from Wadhwani Electronics Laboratory for the support and all the good times we shared. My life at IIT Bombay would have been much less exciting if not for my friends here, Nithin Sankar, Wilson A N, Anakha V B, Renju Boben, Abhijith V S, Reshma Krishnan, Vineesh V S, Sreejith K P, Ramzan Basheer, and Achuth P V. I would like to thank them for the support and all the memories.

To my family, all of this would have been impossible without your love, support and faith in me.
\vspace{0.5cm}

\hspace{11cm}Titto Thomas


\thispagestyle{titlepages}
